\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-09 k-planar.tex
Pffft

\begin{thm}
\label{PowerProduct}
Let $G$ be contained in $H\boxtimes P\boxtimes K_\ell$ with maximum degree $\Delta$, for some graph $H$ of treewidth at most $t$ and for some path $P$. Then for every integer $k\geq 1$, the $k$-th power $G^k$ is contained in $J\boxtimes P\boxtimes K_{2k \ell \Delta^{k}(k^3+3k)}$ for some graph $J$ of treewidth at most $\binom{k+t}{t}-1$ and some path $P$.
\end{thm}

@@

There is a natural drawing of a map graph obtained by positioning each vertex of $G$ inside the corresponding nation and each edge of $G$ as a curve passing through the corresponding vertex of $G_0$. It is easily seen that each edge is in at most $\floor{\frac{d-2}{2}}\ceil{\frac{d-2}{2}}$ crossings; see \citep{dujmovic.eppstein.ea:structure}. Thus $G$ is $(g,\floor{\frac{d-2}{2}}\ceil{\frac{d-2}{2}})$-planar. Also note that \cref{DrawG} with $k=2$ implies that $G$ is $(g, O(d^{2}) )$-planar. \cref{gkPlanarProduct} then establishes a product structure theorem for map graphs, but we get much better bounds by constructing a shortcut system directly.  The following lemma is reminiscent of the characterisation of $(g,d)$-map graphs in terms of the half-square of bipartite graphs \citep{CGP02,dujmovic.eppstein.ea:structure}.

>>>>

\begin{thm}
\label{PowerProduct}
Let $G$ be a graph of maximum degree $\Delta$ that is contained in $H\boxtimes P\boxtimes K_\ell$, for some graph $H$ of treewidth at most $t$ and for some path $P$. Then for every integer $k\geq 1$, the $k$-th power $G^k$ is contained in $J\boxtimes P\boxtimes K_{2k \ell \Delta^{k}(k^3+3k)}$ for some graph $J$ of treewidth at most $\binom{k+t}{t}-1$ and some path $P$.
\end{thm}

@@

There is a natural drawing of a map graph obtained by positioning each vertex of $G$ inside the corresponding nation and each edge of $G$ as a curve passing through the corresponding vertex of $G_0$. It is easily seen that each edge of this drawing is involved in at most $\floor{\frac{d-2}{2}}\ceil{\frac{d-2}{2}}$ crossings; see \citep{dujmovic.eppstein.ea:structure}. Thus $G$ is $(g,\floor{\frac{d-2}{2}}\ceil{\frac{d-2}{2}})$-planar. Also note that \cref{DrawG} with $k=2$ implies that $G$ is $(g, O(d^{2}) )$-planar. \cref{gkPlanarProduct} then establishes a product structure theorem for map graphs, but we get much better bounds by constructing a shortcut system directly.  The following lemma is reminiscent of the characterisation of $(g,d)$-map graphs in terms of the half-square of bipartite graphs \citep{CGP02,dujmovic.eppstein.ea:structure}.
